Investigating Interventions

### 2023-06-14 minos/validation/interventions.Rmd
Updated interventions.Rmd with here package

require(tidyverse)
require(ggplot2)
require(purrr)
require(ordinal)
require(nnet)
require(pscl)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.
```{r}
source('Minos/minos/validation/utils.r')
```

@@

```{r}
out.path <- 'Minos/output/default_config/'
#out.path <- 'Minos/output/scotland_mode/'

base <- read_output(out.path, 'baseline')
allchild <- read_output(out.path, 'hhIncomeChildUplift')
poverty <- read_output(out.path, 'hhIncomePovertyLineChildUplift')
wage <- read_output(out.path, 'livingWageIntervention')
energy <- read_output(out.path, 'energyDownlift')

@@

## Transition Models

```{r, include=FALSE}
trans.path <- 'Minos/data/transitions/'

educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
sf_12.mod <- readRDS(paste0(trans.path, 'SF_12/ols/SF_12_2018_2019.rds'))
house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
income.mod <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
nut.mod <- readRDS(paste0(trans.path, 'nutrition_quality/ols/nutrition_quality_2018_2019.rds'))
```

@@

## Household Income

@@

## Pathways

### Housing Quality

```{r}
compare_housing_out(base, energy)
```

### Neighbourhood Safety

```{r}
compare_neighbourhood_out(base, energy)
```

### Tobacco Use

```{r}
compare_ncigs_out(base, energy)
```

### Nutrition Quality

```{r}
compare_nutrition_out(base, energy)
```

### Loneliness (NOT CURRENTLY IN SF12 MODEL)

```{r}
compare_loneliness_out(base, energy)
```

@@

## Pathways

```{r}
compare_housing_out(base, wage)
compare_neighbourhood_out(base, wage)
compare_ncigs_out(base, wage)
compare_nutrition_out(base, wage)
compare_loneliness_out(base, wage)
```

@@

## Pathways

```{r}
compare_housing_out(base, allchild)
compare_neighbourhood_out(base, allchild)
compare_ncigs_out(base, allchild)
compare_nutrition_out(base, allchild)
compare_loneliness_out(base, allchild)
```

@@

# END

>>>>

require(tidyverse)
require(ggplot2)
require(purrr)
require(here)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.
```{r}
#source('Minos/minos/validation/utils.r')
source(here::here('minos', 'validation', 'utils.r'))
```

@@

```{r}
out.path <- 'Minos/output/default_config/'
#out.path <- 'Minos/output/scotland_mode/'
out.path <- here::here('minos', 'default_config/')

base <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
allchild <- read_singular_local_out(out.path, 'hhIncomeChildUplift', drop.dead = TRUE)
poverty <- read_singular_local_out(out.path, 'hhIncomePovertyLineChildUplift', drop.dead = TRUE)
wage <- read_singular_local_out(out.path, 'livingWageIntervention', drop.dead = TRUE)
energy <- read_singular_local_out(out.path, 'energyDownlift', drop.dead = TRUE)

@@

@@

@@

@@

@@

@@
